---
title: "Unwholesome Consciousness and Stress"
author: "Edward Hillenaar"
date: "2023-07-31"
output: html_document
---
# **Load different R packages**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forcats)
library(gtsummary)
library(gt)
library(ggridges)
library(psych)
library(dplyr)
library(corrr)
```

# **NVM datamatrix and definition "unwholesome" consciousness**

```{r echo=FALSE}
NVM1_Data <- read_delim("D:/DiagnostiekOnderzoek/Data/NVM1_Data.csv", 
                        delim = ";", escape_double = FALSE, trim_ws = TRUE)
NVM <- NVM1_Data
nvm <- NVM
colnames(nvm) <- c("code", "nr", "name", "gender", "age", 
                   "status", "negativism","somatization", "shyness", 
                   "psychopathology", "extraversion")
nvm <- na.omit(nvm)
nvm$consciousness <- ifelse(nvm$psychopathology >= 6, "unwholesome", 
                            ifelse(nvm$psychopathology < 2.0, "wholesome", "neutral"))
nvm$consciousness <- as.factor(nvm$consciousness)
```

# **NVM dataframe**

```{r echo=FALSE}
nvm2 <- nvm %>% 
  select(-c(1:3, 6)) %>% 
  tbl_summary()
```

```{r}
nvm2
```

# **Make a longer dataframe with pivot_longer for visualizations**

```{r echo=FALSE}
long <- nvm %>% 
  select(gender, 
         consciousness, 
         negativism, 
         somatization, 
         shyness, 
         extraversion) %>% 
  pivot_longer(cols = c("negativism", "somatization", "shyness", "extraversion"),
               names_to = "symptoms", values_to = "impact") %>% 
  group_by(consciousness,
           gender,
           symptoms) %>% 
  summarise(avg_impact = mean(impact))
long$symptoms <- as.factor(long$symptoms) 
long$consciousness <- fct_reorder(long$consciousness, long$avg_impact)
long <- as.data.frame(long)
```

# **Create the barplot in ggplot**

```{r echo=FALSE}
plot1 <- long %>% 
    mutate(gender = ifelse(gender == "f", "Female", "Male")) %>% 
    ggplot(aes(consciousness, avg_impact, fill = symptoms)) +
    geom_col(position = "dodge",
           width = .75) +
    scale_x_discrete(expand = c(.3, .3)) +
    scale_fill_manual(values = c("grey90", "grey60", "grey25", "grey1")) +
    facet_wrap(~ gender, strip.position = "bottom") +
    theme_minimal() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank(),
          strip.placement = "outside",
          panel.spacing = unit(0, "cm"),
          legend.position = "bottom",
          strip.text = element_text(size = 20, face = "bold"),
          plot.title.position = "plot",
          plot.title = element_text(size = 24, face = "bold",
                                    margin = margin(b = 20)),
          plot.subtitle = element_text(size = 12, color = "grey30",
                                       margin = margin(b = 20)),
          plot.caption.position = "plot",
          plot.caption = element_text(hjust = 0,
                                      color = "grey50",
                                      size = 10)) +
    labs(fill = "", x = "", y = "Stress Experience",
         caption = "Data from {NVM database} The Vibrational Mind.",
         title = "Consciousness and Behavior",
         subtitle = "The relation between unwholesome consciousness and stress experience by gender.")
```

# **Barchart of consciousness and stress**

```{r}
plot1
```


```{r echo=FALSE}
ggsave("plots/unwholesome_behavior.png", bg = "white")
```
# **Regression model: consciousness as predictor for depression**

```{r echo=FALSE}
nvm$depression <- ifelse(nvm$negativism >= 27 & nvm$somatization >= 22, "depression", "normal")
d = mutate(nvm, unwholesome = as.numeric(consciousness == 'unwholesome'),
           mutate(nvm, depression = as.numeric(depression == 'depression')))
m = glm(depression ~ unwholesome + extraversion + shyness, 
        family=binomial, data = d)
d %>%
  select(unwholesome, depression, extraversion, shyness) %>%
  tbl_uvregression(
    method = glm,
    y = depression,
    method.args = list(family = binomial),
    exponentiate = TRUE
  )
```


# **Theme setting for creating a table**

```{r echo=FALSE}
my_theme <-
  list(
    # Some gt cusomization
    "as_gt-lst:addl_cmds"= list(
      #make the font size small
      tab_spanner = rlang::expr(gt::tab_options(table.font.size = 'small')),
      # add a custom title and subtitle to every table
      user_added1 = rlang::expr(gt::tab_header(
        title = "Depression predicted by Unwholesome Consciousness", 
        subtitle = "Unwholesome Consciousness, Extraversion and Shyness as predictors for Depression")),
      # add a costum data source note
      user_added2 = rlang::expr(gt::tab_source_note(        source_note = "Source: https://github.com/EdwardHill15/Data")),
      # stripe the table rows
      user_added3 = rlang::expr(gt::opt_row_striping())
      #user_added4 = rlang::expr(gt::opt_table_lines("none"))
    )
  )
```

# **Regression model code**

```{r echo=FALSE}
reset_gtsummary_theme()
set_gtsummary_theme(my_theme)

m1 <- glm(
    depression ~ unwholesome + extraversion + shyness,
    data = d,
    family = gaussian()
  )

m1_tbl_n1 <-
  tbl_regression(
    m1, 
    exponentiate = TRUE
  ) %>% 
  add_glance_source_note() %>% 
  add_glance_table(
    include = c(nobs, logLik, AIC, BIC)
  )
```

# **Table regression model**

```{r}
m1_tbl_n1
```


# **Odds ratio's of unwholesome consciousness as a predictor for Depression**

-   The **odds ratio** for **Unwholesome Consciousness** is **`r inline_text(m1_tbl_n1, variable = unwholesome)`**.

-   The **odds ratio** for **Extraversion** is **`r inline_text(m1_tbl_n1, variable = extraversion)`**.

-   The **odds ratio** for **Shyness** is **`r inline_text(m1_tbl_n1, variable = shyness)`**.

